\documentclass[9pt]{extarticle}
\input{formatting}
\usepackage{enumitem}
\usepackage{moresize}
\usepackage[hidelinks]{hyperref}

\begin{document}

% ~~~~~~~~~~~~~~~~
% NAME AND CONTACT
% ~~~~~~~~~~~~~~~~

\begin{minipage}[t]{0.40\textwidth}
	\vspace{-\baselineskip}
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Dan}}}}}\\[2pt]
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Nicholls}}}}}\\[6pt]
	\vspace{6pt}
	{\LARGE AI Software Engineer}
\end{minipage}
\hfill
\begin{minipage}[t]{0.50\textwidth}
	\vspace{-\baselineskip}
		\icon[1em]{MapMarker}{Melbourne, VIC}\\
		\icon[1em]{Envelope}{\href{mailto:dannicholls12@gmail.com}{dannicholls12@gmail.com}}\\
		\icon[1em]{Github}{\href{https://github.com/dan-nicholls}{/dan-nicholls}}\\
		\icon[1em]{Linkedin}{\href{https://www.linkedin.com/in/dannichollsdev/}{/dannichollsdev}}\\
\end{minipage}

\vspace{0.5cm}

% ~~~~~~~~~~~~~~~~
% ABOUT AND SKILLS
% ~~~~~~~~~~~~~~~~

\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}

	\cvsect{Who Am I?}

	I'm an AI Software Engineer working in the Computer Vision space, with a strong interest in object detection, tracking, and media streaming (RTSP, WebRTC, etc.). I enjoy building fast, efficient systems and working close to real-world data.

\end{minipage}
\hfill 
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip}

	\cvsect{Key Skills}

	\begin{tabular}{@{}p{8em} l@{}}
	\textbf{Languages}   & Go, Python, Javascript \\
	\textbf{Frameworks}  & Deepstream, GStreamer, ONNX, PyTorch \\
	\textbf{Eventing}	 & Kafka, Flink, RabbitMQ \\
	\textbf{Automation}  & GitHub Actions, Azure Pipelines \\
	\textbf{Deployment}  & Docker, Azure, AWS \\
	\textbf{OS}          & Linux, Ubuntu, Arch, Nix \\
	\end{tabular}
\end{minipage}

\cvbreak

% ~~~~~~~~~~~~~~~~
% EXPERIENCE
% ~~~~~~~~~~~~~~~~
\begin{minipage}[t]{\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Experience}

	\cvexperience
		{AI Software Engineer}
		{TRU Recognition}
		{Feb 2022 -- Mar 2025}
		{
			\begin{itemize}[itemsep=0.25em]
				\item Led a small AI engineering team to build and deploy a scalable inferencing system using NVIDIA DeepStream and Triton, supporting secure, hardware-aware deployments for both cloud and on-premise use cases.
				\item Managed runtime optimization of object detection models (YOLO, ResNet, CNN) by configuring Triton repositories and tuning performance for real-world tracking in security and retail environments.
				\item Built and standardized CI/CD pipelines across \textasciitilde20 microservices using Azure DevOps, increasing deployment reliability and visibility while reducing failure diagnosis time through automated testing and tracking.
				\item Introduced and led Agile practices across the tech department, running sprint ceremonies, managing cross-functional workflows, and aligning engineering output with sales and product objectives.
				\item Directed the successful integration of a custom API in partnership with a major telecommunications client, enabling seamless and secure device communication across distributed networks.
			\end{itemize}
		}

	\cvexperience
		{Marketing Assistant}
		{Coco Ruby Plastic Surgery}
		{Aug 2016 -- Feb 2022}
		{
			\begin{itemize}[itemsep=0.25em]
    			\item Designed and maintained multiple surgeon websites using WordPress, React, and JavaScript, improving user experience and increasing brand reach.
				\item Implemented SEO strategies with tools like Yoast and Google Analytics to improve search visibility and drive traffic through targeted keyword trends.
				\item Enhanced site performance by optimizing load speed and mobile responsiveness for better accessibility and engagement.
    			\item Managed a large marketing image repository, standardizing metadata to support efficient content management and campaign planning.
			\end{itemize}
		}

	\cvexperience
		{Electronics Engineer Intern}
		{Eco Built Systems}
		{Jun 2018 -- Jul 2018}
		{
			\begin{itemize}[itemsep=0.25em]
				\item Revised technical documentation and resolved hardware issues for a hydroponics lighting system, improving installation reliability and clarity for end users.
				\item Contributed to the design and build of a custom 3D printer, focusing on firmware setup and electronic component troubleshooting during prototyping.
				\item \textit{Completed as a part of the Swinburne Global Internship Program.}
			\end{itemize}
		}
\end{minipage}

\cvbreak

% ~~~~~~~~~~~~~~~~
% EDUCATION 
% ~~~~~~~~~~~~~~~~

\begin{minipage}[t]{\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Education}

	\cveducation
		{Bachelor of Engineering (Electronics \& Computer Systems) \normalfont(Honors)}
		{2015 -- 2021}
		{Swinburne University of Technology}

	\cveducation
		{Bachelor of Computer Science}
		{2015 -- 2021}
		{Swinburne University of Technology}
\end{minipage}

\cvbreak

% ~~~~~~~~~~~~~~~~
% OTHER INFO 
% ~~~~~~~~~~~~~~~~

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Projects}

	This is my projects section
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Hobbies}

	Outside of updating my dotfiles, I enjoy baking sourdough and am currently training to run the Melbourne Marathon.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	\cvsect{References}

	All references to be supplied upon request.
\end{minipage}

\end{document}
